\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-23 draft.tex
Add appendix of tool usage
Abstract and Introduction

@@

MapReduce framework for data-parallel computation was first proposed by Google~\cite{dean04} and later implemented in the Apache Hadoop project~\cite{hadoop}.
Under the MapReduce framework, a reducer computes output values from a sequence of input values transmitted over the network.  Due to the non-determinism in data transmission, the order of input values arrives at the reducer is not fixed.
The \emph{commutativity problem} of reducers asks if the output of a reducer is independent of the order of its inputs. There are several advantages for a reducer being commutative, e.g., the verification problem of a MapReduce program can be reduced to the problem of verifying a sequential program.
We present the tool J-ReCoVer (Java Reducer Commutativity Verifier) that implements effective heuristics for reducer commutativity analysis. J-ReCoVer is the first tool that is specialized in checking reducer commutativity. Experimental results over 118 benchmark examples collected from open repositories are very positive; J-ReCoVer correctly handles over 97\% of them.

@@

\section{Introduction}
\label{section:introduction}

MapReduce is one of the most popular frameworks for data parallel computation.
A MapReduce~\cite{dean04,hadoop} program consists of several pairs of \emph{mappers} and \emph{reducers} running on a machine cluster for handling big data in parallel. Usually, mappers and reducers are the only components in a MapReduce program that involves concurrency. Mappers read data from a distributed database and output a sequence of \emph{key-value} pairs. The sequence elements (key-value pairs) with the same key will be sent to the same reducer for further processing. Due to scheduling policies and network latency, the same inputs may arrive at a reducer in a different order in different executions, which results in the so-called \emph{commutativity problem} of reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}, that is, if the output of a reducer is independent of the order of its inputs.
If all reducers are commutative, they will have the same external behavior under all possible schedules. In such a case, by fixing a schedule, the verification problem of a MapReduce program can be reduced to the verification problem of a sequential program, which is known to be much easier than the verification problem of concurrent programs. One needs to consider only a particular interleaving of input values instead of all of them.

@@

On the other hand, the non-commutative behavior of a reducer is often the source of very tricky bugs. A study conducted by Microsoft investigated the commutativity problem of $508$ reducers running on their MapReduce server~\cite{xiao14mr}. The reducer programs have been checked carefully using all traditional means such as code review, testing, and experiments with real data for months. Still, among them, five programs contain very subtle bugs caused by non-commutativity (confirmed by the programmers).

However, checking reducer commutativity is a difficult problem on its own right~\cite{ChenHSW15,ChenSW16,ChenLTW17}. Even for a simple case that all values are mathematical integers, it is proved undecidable in~\cite{ChenHSW15}. For the case that all values are machine integer (e.g, 64-bits integer), the problem is decidable, but the only available algorithm that was proposed in the same paper is of very high complexity and hence is only of theoretical interests.

In this paper, we present the tool J-ReCoVer (Java Reducer Commutativity Verifier), which is available at~\verb|http://jrecover.iis.sinica.edu.tw|. It implements
heuristics for the commutativity problem that works very efficiently on a large set of practical integer reducer programs. The heuristics reduce the commutativity problem to an SMT problem in a sound but incomplete manner. We also propose optimizations to enable the approach that works on real-world examples. For the case that the reducer is not proven commutative, we complement the approach by using testing to find concrete counterexamples. 
We collected benchmarks from open repositories such as Github and Bitbucket to evaluate J-ReCoVer. With the help of a search engine \emph{searchcode.com} over those repositories, we collected 118 examples. J-ReCoVer is able to correctly analyze all but 3 of them.

@@

>>>>

\usepackage{fancyvrb}
\usepackage[framemethod=tikZ]{mdframed}

@@

The MapReduce framework for data-parallel computation was first proposed by
Google~\cite{dean04} and later implemented in the Apache Hadoop
project~\cite{hadoop}. Under the MapReduce framework, a reducer computes output
values from a sequence of input values transmitted over the network. Due to
non-determinism in data transmission, the order in which input values arrive at
the reducer is not fixed. In relation to this, the \emph{commutativity problem}
of reducers asks if the output of a reducer is independent of the order of its
inputs. Indeed, there are several advantages for a reducer to be commutative,
e.g., the verification problem of a MapReduce program can be reduced to the
problem of verifying a sequential program. We present the tool J-ReCoVer (Java
Reducer Commutativity Verifier) that implements effective heuristics for reducer
commutativity analysis. J-ReCoVer is the first tool that is specialized in
checking reducer commutativity. Our experimental results over 118 benchmark
examples collected from open repositories are very positive; J-ReCoVer correctly
handles over 97~\% of them.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction} \label{section:introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

MapReduce belongs among the most popular frameworks for data parallel
computation. A MapReduce program~\cite{dean04,hadoop} consists of several pairs
of \emph{mappers} and \emph{reducers} running on a machine cluster for handling
big data in parallel. Usually, mappers and reducers are the only components in a
MapReduce program that involve concurrency. Mappers read data from a distributed
database and output a sequence of \emph{key-value} pairs. The elements of the
sequence (i.e., key-value pairs) with the same key are sent to the same reducer
for further processing. Due to scheduling policies and network latency, the same
inputs may arrive at a reducer in different orders in different executions.
Therefore, reducers are typically required to be \emph{commutative}, that is,
the output of a reducer is required to be independent of the order of its
inputs. The problem of checking whether this is indeed the case is known as the
\emph{commutativity problem} of
reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}. If all reducers
are commutative, they will have the same external behavior under all possible
schedules. In such a case, by fixing a schedule, the verification problem of a
MapReduce program can be reduced to the verification problem of a sequential
program, which is known to be much easier than the verification problem of
concurrent programs. One then suffices with considering any chosen interleaving
of input values instead of all of them.

@@

On the other hand, the non-commutative behavior of a reducer is often the source
of very tricky bugs. A study conducted by Microsoft investigated the
commutativity problem of $508$ reducers running on their MapReduce
server~\cite{xiao14mr}. These reducers were carefully checked using all
traditional means such as code review, testing, and experiments with real data
for months. Still, five of these programs contained very subtle bugs caused by
non-commutativity (which was confirmed by the programmers).

However, checking reducer commutativity is a difficult problem on its own
right~\cite{ChenHSW15,ChenSW16,ChenLTW17}. Even for a simple case in which all
values are mathematical integers, it is proved undecidable in~\cite{ChenHSW15}.
For the case when all values are machine integers (e.g., 64-bits integers), the
problem is decidable, but the only available algorithm, which was proposed
in~\cite{ChenHSW15} too, is of very high complexity and hence of theoretical
interest only.

In this paper, we present the J-ReCoVer tool (Java Reducer Commutativity
Verifier), which is available at~\verb|http://jrecover.iis.sinica.edu.tw|. The
tool implements a heuristic approach for checking the commutativity problem
that---despite its simplicity---works very efficiently on a large set of
practical integer reducer programs as shown by our experiments. The main
ingredient of the approach is a reduction from the commutativity problem to an
SMT problem. The reduction is incomplete but sound. It is accompanied with
several heuristics which enable the approach to scale to real-world examples.
For the case when the reducer is not proven commutative, we complement the
approach by using testing to find concrete counterexamples.

We collected benchmarks from open repositories such as Github and Bitbucket to
evaluate J-ReCoVer. With the help of a search engine \emph{searchcode.com} over
those repositories, we collected 118 programs. We provide this collection of
programs to other interested researchers as a side contribution of the paper.
Our tool J-ReCoVer is able to correctly analyze all but three of the programs.

@@

\input{appendix}
